Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-10 manuscript/manuscript.tex
Minor changes in manuscript
Continue writing manuscript: added changes in the power of exponential density

\begin{table}
\caption{
    Description of the synthetic grids on which the comparison of the numerical model against the analytical solutions for a spherical shell was done. This collection of grids tries to include every possible scenario on which the numerical model can present a different behaviour depending on the size of the grid, its location or its height. Every grid consists in a set of 10$\times$10 points.
}
\label{tab:grids}
\begin{tabular}{lcccc}
    Grid & Size & Lat. extension & Lon. extension & Height \\ \hline
    Pole & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Equator & $1^\circ \times 1^\circ$ & $0^\circ - 1^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Satellite & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 260km \\
    Big Grid & $30^\circ \times 30^\circ$ & $60^\circ - 90^\circ$ & $0^\circ - 30^\circ$ & 2km \\
\end{tabular}
\end{table}

@@

>>>>

\begin{table}
\caption{
    Description of the synthetic grids on which the comparison of the numerical model against the analytical solutions for a spherical shell was done. This collection of grids tries to include every possible scenario on which the numerical model can present a different behaviour depending on the size of the grid, its location or its height over the Earth surface. Every grid consists in a set of 10$\times$10 points.
}
\label{tab:grids}
\begin{tabular}{lcccc}
    Grid & Size & Lat. extension & Lon. extension & Height \\ \hline
    Pole & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Equator & $1^\circ \times 1^\circ$ & $0^\circ - 1^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Satellite & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 260km \\
    Big Grid & $30^\circ \times 30^\circ$ & $60^\circ - 90^\circ$ & $0^\circ - 30^\circ$ & 2km \\
\end{tabular}
\end{table}

@@

Because the constant $b$ controls the variation of the density function we wanted to test how does the accuracy of the method behaves at different values of $b$.
We computed the difference between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution on the big grid of 30$^\circ\times$30$^\circ$ (see Table \ref{tab:grids}).
For each value of $b$ we computed these difference for the same set of values of $D$ we've been using on the previous tests, obtaining one curve for each kind of variation.

The results can be seen in Figure \ref{fig:D-exp-power}.
Lower values of $b$ implies a more varying function.
We can see that for extremely varying functions the numerical model does not perform well: for a $b$=100m the difference is almost 100\%.

\todo{poner analisis con respecto al exponente cuando b=1000m}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness and the exponential density defined on equation \ref{eq:density-exp} for different values of $b$. Each computation was performed on the big grid described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power}
\end{figure}
